
\part{Appendices}

\appendix

\renewcommand{\baselinestretch}{1.2}
\normalsize

\chapter{Glossary of \textsc{Matlab} Commands}

\subsection*{Mathematical Operations}
\verb&+  & Addition. Type \verb&help plus& for information.\\
\verb&-  & Subtraction. Type \verb&help minus& for information.\\
\verb&*  & Scalar or matrix multiplication. Type \verb&help mtimes& for information.\\
\verb&/  & Scalar or right matrix division. Type \verb&help slash& for information.\\
\verb&   & For matrices, the command \verb&A/B& is equivalent to \verb&A*inv(B)&.\\
\verb&^  & Scalar or matrix powers. Type \verb&help mpower& for information.\\
\verb&.* & Element by element multiplication. Type \verb&help times& for information.\\
\verb&.^ & Element by element exponentiation. Type \verb&help power& for information.\\
\verb&./ & Element by element division.\\



\subsection*{Built-in Mathematical Constants}
\verb&eps & Machine epsilon, i.e. approximately the computer's floating point
            roundoff error.\\
\verb&i   & $\sqrt{-1}$.\\
\verb&Inf & $\infty$.\\
\verb&NaN & Not a number. Indicates an invalid operation such as $0/0$.\\
\verb&pi  & $\pi = 3.14159 \ldots$.\\


\subsection*{Built-in Mathematical Functions}
\verb&abs(x) & Absolute value$|x|$.\\
\verb&acos(x)& Inverse cosine $\arccos{x}$.\\
\verb&asin(x)& Inverse sine $\arcsin{x}$.\\
\verb&atan(x)& Inverse tangent $\arctan{x}$.\\
\verb&cos(x) & Cosine $\cos{x}$.\\
\verb&cosh(x)& Hyperbolic cosine $\cosh{x}$.\\
\verb&cot(x) & Cotangent $\cot{x}$.\\
\verb&exp(x) & Exponential function $e^x = \exp{x}.$\\
\verb&log(x) & Natural logarithm $\ln{x} = \log_e{x}$.\\
\verb&sec(x) & Secant $\sec{x}$.\\
\verb&sin(x) & Sine $\sin{x}$.\\
\verb&sinh(x)& Hyperbolic sine $\sinh{x}$.\\
\verb&sqrt(x)& Square root $\sqrt{x}$.\\
\verb&tan(x) & Tangent $\tan{x}$.\\
\verb&tanh(x)& Hyperbolic tangent $\tanh{x}$.\\
\verb&max    & Computes maximum of the rows of a matrix.\\
\verb&mean   & Computes the average of the rows of a matrix. \\
\verb&min    & Computes the minimum of the rows of a matrix.


\subsection*{Built-in Numerical Mathematical Operations}
\verb&fzero  & Tries to find a zero of the specified function near a starting point
                or on\\
\verb&       & a specified interval.\\
\verb&inline & Define a function in the command window.\\
\verb&ode113 & Numerical multiple step ODE solver.\\
\verb&ode45  & Runga-Kutta 45 numerical ODE solver.\\
\verb&quad   & Numerical integration using an adaptive Simpson's rule.\\
\verb&dblquad & Double integration.\\
\verb&triplequad & Triple integration.





\subsection*{Built-in Symbolic Mathematical Operations}
\verb&collect & Collects powers of the specified variable is a given symbolic expression.\\
\verb&compose & Composition of symbolic functions.\\
\verb&diff    & Symbolic differentiation.\\
\verb&double  & Displays double-precision representation of a symbolic expression.\\
\verb&dsolve  & Symbolic ODE solver.\\
\verb&expand  & Expands an algebraic expression.\\
\verb&factor  & Factor a polynomial.\\
\verb&int     & Symbolic integration; either definite or indefinite.\\
\verb&limit   & Finds two-sided limit, if it exists.\\
\verb&pretty  & Displays a symbolic expression in a nice format.\\
\verb&simple  & Simplifies a symbolic expression.\\
\verb&subs    & Substitutes for parts a a symbolic expression.\\
\verb&sym& or \verb&syms& Create symbolic variables.\\
\verb&symsum  & Performs a symbolic summation, possibly with infinitely many entries.\\
\verb&taylor  & Gives a Taylor polynomial approximation of a given order at a specified point.\\





\subsection*{Graphics Commands}
\verb&contour   & Plots level curves of a function of two variables.\\
\verb&contourf  & Filled contour plot.\\
\verb&ezcontour & Easy contour plot.\\
\verb&loglog    & Creates a log-log plot.\\
\verb&mesh      & Draws a mesh surface.\\
\verb&meshgrid  & Creates arrays that can be used as inputs in graphics commands \\
\verb&          &  such as \verb&contour&, \verb&mesh&, \verb&quiver&, and \verb&surf&.\\
\verb&ezmesh    & Easy mesh surface plot.\\
\verb&plot      & Plots data vectors.\\
\verb&ezplot    & Easy plot for symbolic functions.\\
\verb&plot3     & Plots curves in 3-D.\\
\verb&polar     & Plots in polar coordinates.\\
\verb&quiver    & Plots a vector field.\\
\verb&semilogy  & Semilog plot, with logarithmic scale along the vertical direction.\\
\verb&surf      & Solid surface plot.\\
\verb&trimesh   & Plot based on a triangulation\\
\verb&trisurf   & Surface plot based on a triangulation





\subsection*{Special \textsc{Matlab} Commands}
\verb&:     & Range operator, used for defining vectors and in loops.\\
\verb&      & Type \verb& help colon& for information.\\
\verb&;     & Suppresses output. Also separates rows of a matrix.\\
\verb&=     & Assigns the variable on the left hand side the value of
                the right hand side.\\
\verb&ans   & The value of the most recent unassigned.\\
\verb&cd    & Change directory.\\
\verb&clear & Clears all values and definitions of variables and functions. You may
             also use to clear only specified variables.\\
\verb&diary & Writes a transcript of a \textsc{Matlab} session to a file.\\
\verb&dir   & Lists the contents in the current working directory. Same as \verb&ls&.\\
\verb&help  &\\
\verb&inline& Define an inline function.\\
\verb&format& Specifies output format, e.g. \verb&> format long&.\\
\verb&load  & Load variables from a file.\\
\verb&save  & Saves workspace variables to a file.\\




\subsection*{\textsc{Matlab} Programming}
\verb&==      & Is equal?\\
\verb&~=      & Is not equal?\\
\verb&<       & Less than?\\
\verb&>       & Greater than?\\
\verb&<=      & Less than or equal?\\
\verb&break   & Breaks out of a \verb&for& or \verb&while& loop.\\
\verb&end     & Terminates an \verb&if&, \verb&for& or \verb&while& statement.\\
\verb&else    & Alternative in an \verb&if& statement.\\
\verb&error   & Displays and error message and ends execution of a program.\\
\verb&for     & Repeats a block of commands a specified number of times.\\
\verb&function& First word in a function program.\\
\verb&if      & Checks a condition before executing a block of statements.\\
\verb&return  & Terminates execution of a program.\\
\verb&warning & Displays a warning message.\\
\verb&while   & Repeats a block of commands as long as a condition is true.\\





\subsection*{Commands for Matrices and Linear Algebra}


{\bf Matrix arithmetic:}\\
\verb&A = [ 1  3 -2 5 ;  -1  -1 5 4 ; 0 1 -9  0]& \dotfill Manually enter a matrix. \\
\verb&u = [ 1  2  3  4]'&\\
\verb&A*u &\\
\verb&B = [3 2 1; 7 6 5; 4 3 2]&\\
\verb&B*A&     \dotfill multiply $B$ times $A$.\\
\verb&2*A&     \dotfill multiply a matrix by a scalar.\\
\verb&A + A&   \dotfill add matrices. \\
\verb&A + 3&   \dotfill add a number to every entry of a matrix. \\
\verb&B.*B&  \dotfill component-wise multiplication. \\
\verb&B.^3&  \dotfill component-wise exponentiation.


{\bf Special matrices:}\\
\verb&I = eye(3)& \dotfill identity matrix\\
\verb&D = ones(5,5)&\\
\verb&O = zeros(10,10)&\\
\verb&C = rand(5,5)& \dotfill random matrix with uniform
         distribution in $[0,1]$.\\
\verb&C = randn(5,5)& \dotfill random matrix with normal distribution.\\
\verb&hilb(6)&\\
\verb&pascal(5)&


{\bf General matrix commands:}\\
\verb&size(C)& \dotfill gives the dimensions ($m \times n$) of $A$.\\
\verb&norm(C)& \dotfill gives the norm of the matrix.\\
\verb&det(C)&   \dotfill the determinant of the matrix.\\
\verb&max(C)&   \dotfill the maximum of each row.\\
\verb&min(C)&   \dotfill the minimum in each row.\\
\verb&sum(C)&   \dotfill sums each row.\\
\verb&mean(C)&   \dotfill the average of each row.\\
\verb&diag(C)&   \dotfill just the diagonal elements. \\
\verb&inv(C)&    \dotfill inverse of the matrix.


{\bf Matrix decompositions:}\\
\verb&[L U P] = lu(C)&\\
\verb&[Q R] = qr(C)&\\
\verb&[U S V] = svd(C)& \dotfill singular value decomposition.





